---
title: "Parallel and iterative evaluation using strmr"
author: "Martin Morgan"
date: "`r Sys.Date()`"
output:
  BiocStyle::html_document
vignette: >
  %\VignetteIndexEntry{Parallel and iterative evaluation using strmr}
  %\VignetteEngine{knitr::rmarkdown}
---

# strmr

The ambition is to easily incorporate parallel evaluation into
magrittr-style 'pipes' in a way that is friendly to large data.

```{r overview, eval=FALSE}
file("my.csv") %>% strm_lapply({
    Sys.sleep(1)  # long computation
    1             # return value
}) %>% plot(formula = result ~ factors)
```

Some level of granularity will be provided by separating the parallel
processing task into three phases: `yield()` up-stream data in
manageable chunks, (lazy) streaming parallel evaluation of chunks via
`strm()`, and reduction of chunks prior to down-stream analysis
(`reduce()`, `ireduce()`).

```{r overview-granular, eval=FALSE}
file("my.csv") %>% yield_csv(size=1e8, by.dim=2) %>% strm({
    Sys.sleep(1)
    1
}) %>% ireduce(sum)
```

Ultimately diverse back-ends will be supported

```{r overview-backend, eval=FALSE}
cores <- backend("multicore", 8)
computer <- backend("socket", 8)
clusters <- backend("mpi")
clouds <- backend("spark")

BamFileList(pattern="bam$") %>% strm_lapply({
    countBam(.)
}, backend=cores) %>% simplify2array()
```

## Progress

- Serial and socket `backend()`
- Vector and by-row `data_strm()`
- Serial `yield1()`

```{r}
suppressPackageStartupMessages({
    library(strmr)
})

## create & register as default
backend(type="serial")

## vector and by-row streams
data_strm(1:10, 3) %>% strm(sqrt) %>% yield1() %>% strmr_value()
data_strm(mtcars, yield.size=4) %>% yield1

## 'yield-all'
s <- strm(data_strm(1:10, 3), sqrt)
repeat {
    s <- yield1(s)
    if (is(strmr_value(s), "strm_done"))
        break
    print(strmr_value(s))
}
strmr_value(s)
```

# Simple parallel evaluation: `strm_lapply_()`

# Greater control with `yield1()`, `strm()`, and `reduce()`

## The `yield()` family

## `strm()`

## The `reduce()` and `reduce_iter()` families
